|

### 2019-03-24 rap/article.Rmd
change pdf viewer

---
title:  |
        | **Deaths and Disappearances in the Pinochet Regime: A New Dataset**
author: 
  - "Danilo Freire[^df]"
  - "John Meadowcroft[^jm]"
  - "David Skarbek[^ds]"
  - "Eugenia Guerrero[^eg]"
date: \today
thanks: "We thank Umberto Mignozzetti and Robert Myles McDonnell for their helpful comments. Data and replication information are available at [`http://github.com/danilofreire/pinochet-data`](http://github.com/danilofreire/pinochet-data)."
abstract: "... However, . This paper presents a georeferenced event dataset on "
keywords: "authoritarian regimes, Chile, georeferenced event data, Pinochet, truth commission"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    template: template.latex
---

@@

Users can download the data as an Excel spreadsheet (`.xlsx`) or as a comma-separated values (`.csv`) file. Both data and codebook are also available to download as an `R` package at <http://github.com/danilofreire/pinochet-data>. The repository has detailed installation instructions for users new to `R`. We follow the principles of "tidy data", where each column represents one variable and each row is one case [@wickham2014tidy].

@@

The third category is _disappearance, information of death_. As the name implies, these observations refer to cases the Commission confirms the individual died after being missing. The formal definition for this category is that "the victims are dead; that they died at the hands of the government agents, or persons in their service; and that these or other agents disposed of the victims' mortal remains by throwing them into a river or a sea, by covertly burying them, or by disposing of them in some other secret fashion" [-@report1991 44]. The assassination of Humberto de las Nieves Fuentes Rodriguez is an example (id number 854). He was taken in custody to the Colina air base, then loaded onto a helicopter with other political prisoners. According to the Report, government agents drugged him, beat him with a metal bar, opened his stomach with a knife before throwing the former Communist alderman from a helicopter. While his body has not been found, there is enough information about the case to classify his death as a severe human rights violation.

@@

@@

>>>>

---
title:  |
        | **Deaths and Disappearances in the Pinochet Regime: A New Dataset**
author: 
  - "Danilo Freire[^df]"
  - "John Meadowcroft[^jm]"
  - "David Skarbek[^ds]"
  - "Eugenia Guerrero[^eg]"
date: \today
thanks: "We thank Umberto Mignozzetti and Robert Myles McDonnell for their helpful comments. Data and replication information are available at [`http://github.com/danilofreire/pinochet`](http://github.com/danilofreire/pinochet)."
abstract: "... However, . This paper presents a georeferenced event dataset on "
keywords: "authoritarian regimes, Chile, georeferenced event data, Pinochet, truth commission"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    template: template.latex
---

@@

Users can download the data as an Excel spreadsheet (`.xlsx`) or as a comma-separated values (`.csv`) file. We have also created an `R` package called `pinochet` which includes the dataset in both formats plus the codebook. The files follow the principles of "tidy data", where each column represents one variable and each row is one case [@wickham2014tidy]. The `pinochet` package is available for download on the Comprehensive R Archive Network (CRAN) and at <http://github.com/danilofreire/pinochet>. To make the data accessible, our GitHub repository has detailed installation instructions for users new to `R`.

@@

The third category is _disappearance, information of death_. As the name implies, these observations refer to cases the Commission confirms the individual died after being missing. The formal definition for this category is that "the victims are dead; that they died at the hands of the government agents, or persons in their service; and that these or other agents disposed of the victims' mortal remains by throwing them into a river or a sea, by covertly burying them, or by disposing of them in some other secret fashion" [@report1991 44]. The assassination of Humberto de las Nieves Fuentes Rodriguez is an example (id number 854). He was taken in custody to the Colina air base, then loaded onto a helicopter with other political prisoners. According to the Report, government agents drugged him, beat him with a metal bar, opened his stomach with a knife before throwing the former Communist alderman from a helicopter. While his body has not been found, there is enough information about the case to classify his death as a severe human rights violation.

@@

[comment]: <> (Table 1 around here)

Although the Report provides a comprehensive list of the regime victims, the Chilean Truth Commission itself acknowledges that the data are incomplete. The Commission had only nine months to write the Report and it had no legal power to oblige citizens to cooperate. Therefore, we expect that some cases have not been recorded. But this problem is not unique to the Pinochet regime. Selection bias is a common feature in events data, even more so in datasets about armed conflict or government repression [@ball2019using; @chapman2001truth]. As the cases might not be a representative sample of the population of victims, we suggest scholars to carefully consider issues of model specification.

@@

We have georeferenced all observations for which the relevant data was available.
